Modeling Two-Dimensional Vesicle Hydrodynamics with Hydrophobic Attraction Potential Simulations

### 2021-09-15 doc/main_jfm.tex

This study presents a coarse-grained model for JP vesicles that focuses
on the hydrophobic interactions between coarse-grained lipids and
hydrodynamic interactions. In contrast to molecular dynamic simulations,
the hydrophobic interactions exhibit the self-assembly property of the
lipid bilayer membrane. The proposed energy potential combined with the
mobility problem for rigid body motions captures membrane mechanics
including deformations, stretching modulus, and permeability of a JP
membrane. This work is highly applicable with fields in material science
and condensed matter physics such as Janus
colloids~(\cite{Bradley2017,Mallory2017}) and the setup can be tuned to
match experimental results such as the morphology of colloid
surfactants~(\cite{Bradley2016}). 
%
For instances, with the flexibility of the model, we can manage a specific boundary condition
of particle surfaces based on the chemicals chosen in experiments. This can be an assist to 
study of interparticle interactions and chemical compositions in industry.

Integral equation methods are used to solve the mobility problem and the
previously introduced HAP model. We describe a method to calculate the
hydrophobic forces and torques on each individual rigid body that avoids
singular integrals. In addition to the HAP forces and torques, we use a
short-range repulsion to avoid unphysical contact. Our method requires
calculations of the hydrodynamic stress tensor, and these are used to
estimate the membrane permeability constant $P$ and the membrane
stretching modulus $K_A$. With the use of suitable parameters, the
numerical results yield qualitative phenomena such as a tank-treading JP
vesicle. The reduced area $A^*$ decreases as the shear rate increases
and we measure the equilibrium reduced area for various shear rates. The
results show that the total length of a JP vesicle is conserved and the
decay rate of the reduced area is independent of the shear rate values
between $0.005$~ns$^{-1}$ and~$0.008$~ns$^{-1}$. Moreover, the proposed
model can describe membrane rupture in high shear rates. Therefore, our
method can be applied to vesicles undergoing topological changes which
is difficult to simulate when using a continuum model that represents
vesicles as closed and continuous curves.

Our coarse-grained model is also able to calculate inter-monolayer
friction. The inter-monolayer friction coefficient is determined by
calculating the tangential friction force and slip velocities with
respect to the bilayer midplane. The resulting friction coefficients are
about an order of magnitude smaller than those reported
by~\cite{denOtter2007}, and this discrepancy is partially due to the
granularity of our model. In addition, the coarse-graining level of the
JP vesicle has a much larger length scale than molecular dynamics
simulations, and the repulsive force creates gaps between Janus
particles where the error in slip velocities accumulates over time.

We also study the spatial migration of a JP vesicle suspended in a
parabolic flow. The chosen parameter values result in an asymmetric
slipper shape. While the initial reduced area of the JP vesicle is $A^*
\approx 1$, the equilibrium reduced area is $A^*=0.9$. A qualitative
agreement is made by comparing the JP vesicle shape with the
two-dimensional inextensible membrane in continuum modeling
simulations~(\cite{Kaoui09, dan-vla-mis2009, cou-kao-pod-mis2008}). An
interesting result of the JP vesicle is that $y$-coordinate of the
centroid oscillates at a value slightly above the center of the
Poiseuille flow. This may be caused by the granularity of the JP vesicle
and choices of the model parameters.

The single JP vesicle simulations end with obtaining JP bilayer stretching 
modulus $K_A$ and hydraulic permeability constant $P$. We extract these 
physical quantities from the Laplace pressure relationship that $R\Delta P$ is 
proportional to JP bilayer stretch. We describe the aqueous flux in membrane 
using a differential equation~\ref{eq:perm} and solve for the theoretical 
permeability constant $P$. In spite of producing these values with some discrepancy
using the default parameter set, we provide a new framework in measuring coarse-grained 
membrane permeability.

We compare setups of two JP vesicles and two vesicles described with a
continuum model. A comparison of the vesicle shapes and the streamlines
demonstrate remarkable similarities. The two overlapping trajectories of
the JP vesicles' centroids in a shear flow evolve as expected when the
two centroids are initialized on the same horizontal level. We also
observe a rotating behavior that is observed for models involving
vesicle adhesion~(\cite{qua-vee-you2019}). The hydrophobic action and
the repulsive potential lead to this adhesive effect when two JP
bilayers are sufficiently close. We also perform four simulations of two
JP vesicles suspended in an extensional flow. We vary the initial
vertical displacement of the vesicles' centroids and obtain similar
results to the continuum model.

>>>>

In \cite{Fu20} a mathematical model is developed to quantify the macroscopic assembly and mechanics of 
a JP bilayer in a viscous solvent. The interactions between JPs are formulated as a second-kind integral equation, which is coupled to the incompressible Stokes equations for the surrounding incompressible fluid at the zero-Reynolds-number limit.  Numerical simulations of a JP suspension reveal self-assembly of JPs into micelles and bilayers, and also provide an alternative means for computing the mechanical moduli of a JP membrane, which often requires the knowledge of an equation of state from experiments on a colloidal membrane~(\cite{Balchunas2019_SM}).
In this study we used this integral formulation and numerical algorithm to simulate the hydrodynamics of JP vesicles. 
%
%This study presents a coarse-grained model for JP vesicles that focuses
%on the hydrophobic interactions between coarse-grained lipids and
%hydrodynamic interactions. In contrast to molecular dynamic simulations,
%the hydrophobic interactions exhibit the self-assembly property of the
%lipid bilayer membrane. The proposed energy potential combined with the
%mobility problem for rigid body motions captures membrane mechanics
%including deformations, stretching modulus, and permeability of a JP
%membrane. 
%
Results in this work show great potential to study Janus colloids~(\cite{Bradley2017,Mallory2017}) and the morphology of colloid
surfactants~(\cite{Bradley2016}). 
%
%This work is highly applicable with fields in material science
%and condensed matter physics such as Janus
%colloids~(\cite{Bradley2017,Mallory2017}) and the setup can be tuned to
%match experimental results such as the morphology of colloid
%surfactants~(\cite{Bradley2016}). 
%%
For example, with the flexibility of the model, we can specify the boundary condition on JP surfaces based on the chemicals used in experiments. 
%This can be an assist to study of interparticle interactions and chemical compositions in industry.

%Integral equation methods are used to solve the mobility problem and the
%previously introduced HAP model. We describe a method to calculate the
%hydrophobic forces and torques on each individual rigid body that avoids
%singular integrals. In addition to the HAP forces and torques, we use a
%short-range repulsion to avoid unphysical contact.

In\S~\ref{subsec:calculating_force} we derived an alternative integral form for calculating the force and torque to avoid the singular integral evaluation. These alternative integrals allow us to 
%
%Our method requires
%calculations of the hydrodynamic stress tensor, and these are used to
%
estimate the inter-monolayer friction, membrane permeability constant $P$ and the membrane
stretching modulus $K_A$. 
The inter-monolayer friction coefficient is determined by
calculating the tangential friction force and slip velocities with
respect to the bilayer mid-plane. The resulting friction coefficients are
about an order of magnitude smaller than those reported
by~\cite{denOtter2007}, and this discrepancy is partially due to the
granularity of our model. In addition, the coarse-graining level of the
JP vesicle has a much larger length scale than molecular dynamics
simulations, and the repulsive force creates gaps between Janus
particles where the error in slip velocities accumulates over time.

Under a linear shear flow, we found a JP vesicle to exhibit elongation and tank-treading dynamics observed for a lipid bilayer GUV.
%
%With the use of suitable parameters, the
%numerical results yield qualitative phenomena such as a tank-treading JP
%vesicle. 
%
The reduced area $A^*$ decreases as the shear rate increases
and we measure the equilibrium reduced area for various shear rates. The
results show that the total length of a JP vesicle is conserved and the
decay rate of the reduced area is independent of the shear rate values
between $0.005$~ns$^{-1}$ and~$0.008$~ns$^{-1}$. Moreover, the proposed
model can describe membrane rupture in high shear rates. Therefore, our
method can be applied to vesicles undergoing topological changes which
is difficult to simulate when using a continuum model that represents
vesicles as closed and continuous curves.
%
%Our coarse-grained model is also able to calculate inter-monolayer
%friction. 
%

We also simulate the spatial migration of a JP vesicle in a
parabolic shear flow. 
%The chosen parameter values result in an asymmetric
%slipper shape. 
%
Similar to the hydrodynamics of a GUV in a Poiseuille flow~(\cite{Kaoui09, dan-vla-mis2009, cou-kao-pod-mis2008}),
the nano JP vesicle moves toward the center of the shear flow.
While the initial reduced area of the JP vesicle is $A^*
\approx 1$, the equilibrium reduced area is $A^*=0.9$. 
For the parameters we used in the simulation, the JP vesicle takes an asymmetric shape as it settles above the center of flow and exhibits tank-treading motion.
%A qualitative
%agreement is made by comparing the JP vesicle shape with the
%two-dimensional inextensible membrane in continuum modeling
%simulations~(\cite{Kaoui09, dan-vla-mis2009, cou-kao-pod-mis2008}). 
An
interesting result of the JP vesicle is that $y$-coordinate of the
centroid oscillates at a value slightly above the center of the
Poiseuille flow. This may be caused by the granularity of the JP vesicle
and choices of the model parameters.

%The single JP vesicle simulations end with obtaining JP bilayer stretching 
%modulus $K_A$ and hydraulic permeability constant $P$. We extract these 
%physical quantities from the Laplace pressure relationship that $R\Delta P$ is 
%proportional to JP bilayer stretch. We describe the aqueous flux in membrane 
%using a differential equation~\ref{eq:perm} and solve for the theoretical 
%permeability constant $P$. In spite of producing these values with some discrepancy
%using the default parameter set, we provide a new framework in measuring coarse-grained 
%membrane permeability.

We further simulate the hydrodynamics of  two JP vesicles, and draw comparison with simulation results of two vesicles described by the Helfrich
continuum model. A comparison of the vesicle shapes and the streamlines
demonstrate remarkable similarities. The two overlapping trajectories of
the JP vesicles' centroids in a shear flow evolve as expected when the
two centroids are initialized on the same horizontal level. We also
observe a rotating behavior that is observed for models involving
vesicle adhesion~(\cite{qua-vee-you2019}). The hydrophobic action and
the repulsive potential lead to this adhesive effect when two JP
bilayers are sufficiently close. We also perform four simulations of two
JP vesicles suspended in an extensional flow. We vary the initial
vertical displacement of the vesicles' centroids and obtain similar
results to the continuum model.
